---
title: "Who Represents You?"
output:
  html_document: default
css: styles.css
---
# Your Elected Officials

```{r init, include=FALSE}
## load API keys
source("keys.R")
## you may also load necessary libraries and set various options here
library(dplyr)
library(ggplot2)
knitr::opts_chunk$set(error=TRUE)
                           # continue compiling on error
```

```{r address, include=FALSE}
## insert your address here.  It does not to have quite complete.
## Test your code with addresses in different states, see if it works
address <- "San Francisco, CA"
```
This is a report about the elected officials for residents of `r address`. This report draws upon data from the [Google Civic Data API](https://projects.propublica.org/api-docs/congress-api/). As an overview, here is a summary of *who* represents the address given (from the national to the local level).
```{r, echo=FALSE}
## Make the main computations here.  Keep the functions in a separate file(s)
## and only include the final operations here.
## You have to 'source()' your main R file(s) here:
source('process_data.R')
## You may also have to do some additional processing here

electedOfficials <- select(electedOfficials, Names = name, Position = electedOffices,
                           Party = party, Email = emails, 
                           Phone = phones, Photo = photoUrl)

knitr::kable(electedOfficials)
```

## Your Representatives

Now let’s take a look at **all** of the congressional representatives (in the House of Representatives, *not* the Senate) for California state where the address was given. It has a total number of representatives of `r stateRepresentatives %>% nrow()`. This report draws upon data from the [ProPublica API](https://projects.propublica.org/api-docs/congress-api/).

```{r, echo=FALSE}
## You may want to print the table in a nice way using `knitr::kable()`
## when you have already created it.
knitr::kable(repTable)
```

## House of Representatives

Now let’s take a look at California's breakdown by political party and seniority for those members of the House. This report draws upon data from the [ProPublica API](https://projects.propublica.org/api-docs/congress-api/).

```{r, echo=FALSE}
ggplot(data=party.df, aes(x=Party, y=n, fill=Party, alpha=0.7)) + 
  geom_bar(stat="identity") + coord_flip() + ylab("# of Representatives") +
  scale_fill_manual("Party", values = c("R" = "red", "D"= "blue")) + theme(legend.position="none")
```

This graph shows the partisan distribution amongst the house representatives within the state of California.

```{r, echo=FALSE}
ggplot(data=seniority.df, aes(x=Seniority, y=n, alpha=0.7)) + geom_bar(stat="identity") + theme(legend.position="none") + xlab("Seniority by years") + ylab("# of Representatives")
```

This graph shows the seniority distribution amongst the house representatives within the state of California.

## Linda Sánchez

Let’s learn a bit more about one representative, *Linda Sánchez*. The representative is `r linda.party`, `r linda.age` years old, and you can find them on twitter at [`r linda$twitter_account`](https://twitter.com/`r linda$twitter_account`). Interestingly, of the last 20 congressional votes, the representative was in accordance with the majority `r majority.pct`% of the time.

