---
title: "UFO sightings"
output: html_document
---

```{r setup, include = FALSE}
library(dplyr)
library(ggplot2)
library(maps)
library(mapdata)

knitr::opts_chunk$set(echo = TRUE)
source("summary.r")
source("chart1.r")
source("chart2.r")

ufo.data <- read.csv("../data/UFOCoords.csv", na.strings = c("NA","N/A",""), stringsAsFactors = FALSE)
```

## UFO Sightings Summary

```{r summary, include = FALSE}
summary(ufo.data)
```

From the data we can see that **California** had the *most sightings in the US*. Across the border, in *Canada*, the province with the most sightings was **Ontario**. We can also find the most reported shape. The *most* reported shape was the **cone** while the *least* reported shape was a **light**. In the *AM* people said they saw something at **midnight**. In the *evening* the most reported time was **9pm**.

## UFO Shapes in Sightings
```{r, echo = FALSE, message = FALSE}
plot(chart_1_func(ufo.data))
```

## Times of UFO Sightings
```{r, echo = FALSE, message = FALSE}
plot(chart_2_func(ufo.data))
```
